
\documentclass{IOS-Book-Article}

\usepackage{mathptmx}
\usepackage{soul}\setuldepth{article}
<<<<<<< HEAD
\usepackage{booktabs}
=======
 
>>>>>>> 7c1cec024806f0122dbd3ebada2b3244dc9de7ab
%\usepackage{times}
%\normalfont
%\usepackage[T1]{fontenc}
%\usepackage[mtplusscr,mtbold]{mathtime}
%
<<<<<<< HEAD
\def\hb{\hbox to 10.7 cm{}}
=======
\usepackage{graphicx}
\usepackage{hyperref}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
\setlength{\parskip}{0pt}
\raggedbottom
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{csquotes}
\usepackage{paralist}
\usepackage{booktabs}
\usepackage{mathptmx}
>>>>>>> 7c1cec024806f0122dbd3ebada2b3244dc9de7ab
\usepackage{pgfplots}
\pgfplotsset{compat=1.8}
\usepackage{subfigure}
\pgfplotsset{width=7cm,compat=1.8}
\usepackage{pgfplotstable}
<<<<<<< HEAD
\renewcommand*{\familydefault}{\sfdefault}
\usepackage{tikz}
\usepackage{multirow}
\begin{document}
\pagestyle{headings}
\def\thepage{}

\begin{frontmatter}              % The preamble begins here.


%\pretitle{Pretitle}
\title{Prediction of Malaria with Machine Learning
Algorithms : An experimental Study}

\markboth{}{November 2020\hb}
%\subtitle{Subtitle}

\author[A]{\fnms{Oussseynou} \snm{MBAYE}%
\thanks{Corresponding Author: Book Production Manager, IOS Press, Nieuwe Hemweg 6B,
1013 BG Amsterdam, The Netherlands; E-mail:
bookproduction@iospress.nl.}},
\author[B]{\fnms{Mamadou Lamine } \snm{BA}}
and
\author[B]{\fnms{Alassane} \snm{SY}}

\runningauthor{O. MBAYE et al.}
\address[A]{ALioune Diop University of Bambey }
\address[B]{ALioune Diop University of Bambey}

\begin{abstract}
Still today, Malaria remains one of the most feared diseases in Sub- Saharan Africa and especially in Senegal. This is mainly due to inappropriate medical care support coupled with an often late and error-prone diagnosis from the medical staff. In addition, largely used diagnostic standards such as the Rapid Diagnosis Test is not fully reliable. With the development and increasing adoption of automated tools in the health field, machine learning applications might help medical actors in their decision-making process. In this paper, we propose an experimental study of six machine learning algorithms for the prediction of Malaria in Senegal. These algorithms aim at predicting whether or not a given patient suffers from Malaria based on his signs and symptoms. The performance of the algorithms have been extensively tested and evaluated over real data sets about patients in Senegal that suffer or not from Malaria. The algorithms are evaluated using four criteria: accuracy, Recall, F-measure, Precision and Specificity. The research has shown that there is not necessarily a single best classification tool, but instead the best performing algorithm will depend on the dataset to be analysed
\end{abstract}

\begin{keyword}

\end{keyword}
\end{frontmatter}
%\markboth{January 2020\hb}{January 2020\hb}
%\thispagestyle{empty}
%\pagestyle{empty}

% Introduction
\input{Introduction}

% Prediction Model
\input{Methods}
% Related work
\input{Results}

% Data Preparation
\input{Discussion}
\input{Conclusion}


\begin{thebibliography}{99}
%\bibliography{IOS-Book-Article}
\end{thebibliography}
=======
%\renewcommand*{\familydefault}{\sfdefault}
\usepackage{tikz}

\def\hb{\hbox to 10.7 cm{}}

\begin{document}

\pagestyle{headings}
\def\thepage{}

\begin{frontmatter}              % The preamble begins here

%\pretitle{Pretitle}
\title{On the efficiency of Machine Learning Models in predicting Malaria using Sympt\^om Data}

\markboth{}{January 2020\hb}
%\subtitle{Subtitle}

\author{\fnms{Ousseynou} \snm{Mbaye}},
\author{\fnms{Mouhamadou Lamine} \snm{BA}
\thanks{Corresponding Author: Mouhamadou Lamine BA, LIMA, Universit\'e Alioune Diop,
BP.3400 Bambey, Senegal; E-mail: mouhamadoulamine.ba@uadb.edu.sn.}}
and
\author{\fnms{Alassane} \snm{SY}}

\runningauthor{O.Mbaye et al.}
\address{LIMA, Universit\'e Alioune Diop, Bambey, Senegal}
%\address[B]{Short Affiliation of Second Author and Third Author}

\begin{abstract}
Still today, Malaria remains one of the most feared diseases in Sub-Saharan Africa and especially in Senegal. This is mainly due to inappropriate medical care support coupled with an often late and error-prone diagnosis from the medical staff. In addition, largely used diagnostic standards such as the Rapid Diagnosis Test is not fully reliable. With the development and increasing adoption of automated tools in the health field, machine learning applications might help medical actors in their decision-making process. In this paper, we propose an experimental study of six machine learning algorithms for the prediction of Malaria in Senegal. These algorithms aim at predicting whether or not a given patient suffers from Malaria based on his signs and symptoms. The performance of the algorithms have been extensively tested and evaluated over real data sets about patients in Senegal that suffer or not from Malaria. The algorithms are evaluated using four criteria: accuracy, Recall, F-measure, Precision and Specificity. The research has shown that there is not necessarily a single best classification tool, but instead the best performing algorithm will depend on the dataset to be analysed.
\end{abstract}

\begin{keyword}
electronic camera-ready manuscript\sep IOS Press\sep
\LaTeX\sep book\sep layout
\end{keyword}
\end{frontmatter}
\markboth{January 2020\hb}{January 2020\hb}
%\thispagestyle{empty}
%\pagestyle{empty}

\input{../intro}

\input{../related_work}

\input{../Algorithme}

\input{../datasets}

\input{../experimentation}

\input{../conclusion}





\bibliographystyle{vancouver}
\bibliography{../biblio}

>>>>>>> 7c1cec024806f0122dbd3ebada2b3244dc9de7ab
\end{document}
